---
title: "20170627_THP1_LAMP1_LC3"
author: "MANISHA"
date: "June 27, 2017"
output: 
    html_document: 
        code_folding: hide
        fig_caption: yes
        fig_height: 8
        fig_width: 12
        fontsize: 10pt
        toc_float: 
        collapsed: false    
        smooth_scroll: FALSE
---

# Load the config

In this file there is experiment that is analysed.
- IMAGING - Z - PERKIN ELMER


This experiments was performed by Manisha in PE SPINNING DISC to check the  effects of 3 compounds (test+dmso) at 1 doses - 10uM & 1 timepoint - 48 hrs on THP1 macrophages upon infection - H37Ra, BCG, Smegmatis.

```{r, eval=TRUE, message=FALSE, warning=FALSE}
library(magrittr)
library(dplyr)
library(ggplot2)
source("R/ggtheme_jack.R")
source("R/fun_multiplot.R")
ggplot2::theme_set(theme_jack())

stats_mean <- "TRUE"
filter_mean <- "TRUE"
fit_plots <- "TRUE"

base_path <- c("../../../data")

exp_name <- c("170627_20170619_lamp1_lc3_thp1")


dat <- readr::read_csv(sprintf("%s/%s.csv",base_path, exp_name))



```


# select the data

```{r, message=FALSE, eval=stats_mean}


dat %<>%
  select(
    contains("Metadata"),
    contains("Children"),
    contains("AreaShape_Area"),
    contains("Intensity_IntegratedIntensity"),
    contains("Object_Number")
    )

dat %<>% 
  select(
    -contains("Edge"), 
    -contains("Frame"), 
    -contains("Channel"),
    -contains("Site"),
    -contains("FileLocation"),
    -contains("ColorFormat"),
    -contains("Plate"),
    -contains("Size")
    )


```


# filter the data

```{r, message=FALSE, eval=filter_mean}


p1 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigBCH)) + geom_density() + xlim(0,3000)
p2 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigGCH)) + geom_density() + xlim(0,2000)
p3 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigRCH)) + geom_density() + xlim(0,2000)
p4 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigDRCH)) + geom_density() + xlim(0,2000)

multiplot(p1,p2,p3,p4, cols = 2)

n1 <- nrow(dat)

dat %<>% 
  filter(Intensity_IntegratedIntensity_OrigBCH > 10 & Intensity_IntegratedIntensity_OrigBCH < 3000)
n2 <- nrow(dat)

n1
n2

cells_filtered <- (n1-n2)*100/n1

sprintf("Percentage of cells filtered out: %s", cells_filtered)


p1 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigBCH)) + geom_density() + xlim(0,3000)
p2 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigGCH)) + geom_density() + xlim(0,2000)
p3 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigRCH)) + geom_density() + xlim(0,2000)
p4 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigDRCH)) + geom_density() + xlim(0,2000)


multiplot(p1,p2,p3,p4, cols = 2)

```

# name to plot the data

```{r, message=FALSE, eval=fit_plots}

unique(dat$Children_GCH_Count)

dat$Metadata_InfStatus[dat$Children_GCH_Count == 0] <-  "Uninf" 
dat$Metadata_InfStatus[dat$Children_GCH_Count > 0] <-  "Inf" 

unique(dat$Metadata_InfStatus)

dat$Metadata_Status <- paste(dat$Metadata_Treatment, dat$Metadata_InfStatus, sep="_")

unique(dat$Metadata_Status)

```



# plot the data - LC3 INTENSITY

```{r, message=FALSE, eval=fit_plots}



p1 <-
  ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + ylim(0,1000) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LC3 positive vesicles intensity at 48 hpi",
    y="Whole Cell Int-Intensity of LC3 positive vesicles",
    x="COMPOUND TREATMENT")

p2 <- ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + ylim(0,1000) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LC3 positive vesicles intensity at 48 hpi",
    y="Whole Cell Int-Intensity of LC3 positive vesicles",
    x="COMPOUND TREATMENT")


multiplot(p1,p2, cols = 1)

```



# plot the data - LC3 COUNT

```{r, message=FALSE, eval=fit_plots}



p1 <- ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_InfStatus,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,100) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LC3 positive vesicles count at 48 hpi",
    y="Count of LC3 positive vesicles",
    x="COMPOUND TREATMENT")

p2 <- ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_InfStatus,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,100) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LC3 positive vesicles count at 48 hpi",
    y="Count of LC3 positive vesicles",
    x="COMPOUND TREATMENT")


multiplot(p1,p2, cols = 1)



```



# plot the data - LAMP1 INTENSITY

```{r, message=FALSE, eval=fit_plots}


p1 <- ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,1000) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")

p2 <- ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_InfStatus,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,1000) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")


multiplot(p1,p2, cols = 1)



```

# plot the data - LAMP1 COUNT

```{r, message=FALSE, eval=fit_plots}

p1 <- ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_InfStatus,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,100) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi",
    y="Count of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")

p2 <- ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_InfStatus,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,100) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Treatment) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi",
    y="Count of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")


multiplot(p1,p2, cols = 1)


```

# plot the data - FINAL PLOTS - BCG

```{r, message=FALSE, eval=fit_plots}


ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + ylim(0,2500) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LC3 positive vesicles intensity at 48 hpi in BCG",
    y="Whole Cell Int-Intensity of LC3 positive vesicles",
    x="COMPOUND TREATMENT")


ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,150) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LC3 positive vesicles count at 48 hpi in BCG",
    y="Count of LC3 positive vesicles",
    x="COMPOUND TREATMENT")


ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,4000) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in BCG",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")



ggplot(dat %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,100) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in BCG",
    y="Count of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")


```

# plot the data - FINAL PLOTS - H37Ra

```{r, message=FALSE, eval=fit_plots}


ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + ylim(0,2500) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LC3 positive vesicles intensity at 48 hpi in H37Ra",
    y="Whole Cell Int-Intensity of LC3 positive vesicles",
    x="COMPOUND TREATMENT")


ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,150) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LC3 positive vesicles count at 48 hpi in H37Ra",
    y="Count of LC3 positive vesicles",
    x="COMPOUND TREATMENT")


ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,4000) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in H37Ra",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")



ggplot(dat %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,100) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in H37Ra",
    y="Count of LAMP1 positive vesicles",
    x="COMPOUND TREATMENT")


```



```{r, eval = fit_plots}


dat1 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 0 & Intensity_IntegratedIntensity_OrigRCH < 250)

dat2 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 250 & Intensity_IntegratedIntensity_OrigRCH < 500)

dat3 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 500 & Intensity_IntegratedIntensity_OrigRCH < 750)

dat4 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 750 & Intensity_IntegratedIntensity_OrigRCH < 1000)




ggplot(dat1 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,25) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in BCG",
    y="Count of LAMP1 positive vesicles in bin 1",
    x="COMPOUND TREATMENT")


ggplot(dat2 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,50) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in BCG",
    y="Count of LAMP1 positive vesicles in bin 2",
    x="COMPOUND TREATMENT")


ggplot(dat3 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,80) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in BCG",
    y="Count of LAMP1 positive vesicles in bin 3",
    x="COMPOUND TREATMENT")

ggplot(dat4 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,85) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in BCG",
    y="Count of LAMP1 positive vesicles in bin 4",
    x="COMPOUND TREATMENT")

#######

ggplot(dat1 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,1250) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in BCG",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 1",
    x="COMPOUND TREATMENT")


ggplot(dat2 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,2500) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in BCG",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 2",
    x="COMPOUND TREATMENT")


ggplot(dat3 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in BCG",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 3",
    x="COMPOUND TREATMENT")


ggplot(dat4 %>% filter(Metadata_Infection == "bcg"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in BCG",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 4",
    x="COMPOUND TREATMENT")



########


ggplot(dat1 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,25) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in H37Ra",
    y="Count of LAMP1 positive vesicles in bin 1",
    x="COMPOUND TREATMENT")


ggplot(dat2 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,50) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in H37Ra",
    y="Count of LAMP1 positive vesicles in bin 2",
    x="COMPOUND TREATMENT")


ggplot(dat3 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,80) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in H37Ra",
    y="Count of LAMP1 positive vesicles in bin 3",
    x="COMPOUND TREATMENT")

ggplot(dat4 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,85) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles count at 48 hpi in H37Ra",
    y="Count of LAMP1 positive vesicles in bin 4",
    x="COMPOUND TREATMENT")

#######

ggplot(dat1 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,1250) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in H37Ra",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 1",
    x="COMPOUND TREATMENT")


ggplot(dat2 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,2500) +
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in H37Ra",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 2",
    x="COMPOUND TREATMENT")


ggplot(dat3 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in H37Ra",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 3",
    x="COMPOUND TREATMENT")


ggplot(dat4 %>% filter(Metadata_Infection == "ra"),
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  facet_grid( ~ Metadata_Infection) +
  labs(
    title="LAMP1 positive vesicles intensity at 48 hpi in H37Ra",
    y="Whole Cell Int-Intensity of LAMP1 positive vesicles in bin 4",
    x="COMPOUND TREATMENT")




```
