---
title: "20170716_THP1_BCG_dextran_dqbsa_02hrs"
author: "MANISHA"
date: "July 17, 2017"
output: 
    html_document: 
        code_folding: hide
        fig_caption: yes
        fig_height: 8
        fig_width: 12
        fontsize: 10pt
        toc_float: 
        collapsed: false    
        smooth_scroll: FALSE
---

# Load the config

In this file there is experiment that is analysed.
- IMAGING - Z - PERKIN ELMER


This experiments was performed by Manisha in PE SPINNING DISC to check the  effects of 3 compounds (test+dmso) at 1 doses - 10uM & 1 timepoint - 02 hrs on THP1 macrophages upon infection -  BCG.

```{r, eval=TRUE, message=FALSE, warning=FALSE}
library(magrittr)
library(dplyr)
library(ggplot2)
source("R/ggtheme_jack.R")
source("R/fun_multiplot.R")
ggplot2::theme_set(theme_jack())

stats_mean <- "TRUE"
filter_mean <- "TRUE"
fit_plots <- "TRUE"

base_path <- c("../../../data")

exp_name_file <- c("20170716_THP1_BCG_dextran_dqbsa_02hrs_Cells")
exp_name_layout <- c("20170716_THP1_BCG_dextran_dqbsa_02hrs_layout")

dat <- readr::read_csv(sprintf("%s/%s.csv",base_path, exp_name_file))


dat_layout <- readr::read_csv(sprintf("%s/%s.csv",base_path, exp_name_layout))


dat <- inner_join(dat,dat_layout, by = "Metadata_Series")


```
# name to plot the data

```{r, message=FALSE, eval=fit_plots}

unique(dat$Children_GCH_Count)

dat$Metadata_InfStatus[dat$Metadata_Infection == "INF" & dat$Children_GCH_Count == 0] <-  "Bystander" 
dat$Metadata_InfStatus[dat$Metadata_Infection == "INF" & dat$Children_GCH_Count > 0] <-  "Inf" 
dat$Metadata_InfStatus[dat$Metadata_Infection == "UNINF" & dat$Children_GCH_Count == 0] <-  "Unexp"
dat$Metadata_InfStatus[dat$Metadata_Infection == "UNINF" & dat$Children_GCH_Count > 0] <-  "Inf"

unique(dat$Metadata_InfStatus)

dat$Metadata_Status <- paste(dat$Metadata_Treatment, dat$Metadata_InfStatus, sep="_")

unique(dat$Metadata_Status)

```

# select the data

```{r, message=FALSE, eval=stats_mean}


dat %<>%
  select(
    contains("Metadata"),
    contains("Children"),
    contains("AreaShape_Area"),
    contains("Intensity_IntegratedIntensity"),
    contains("Object_Number")
    )

dat %<>% 
  select(
    -contains("Edge"), 
    -contains("Frame"), 
    -contains("Channel"),
    -contains("Site"),
    -contains("FileLocation"),
    -contains("ColorFormat"),
    -contains("Plate"),
    -contains("Size")
    )


```


# filter the data

```{r, message=FALSE, eval=filter_mean}


p1 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigBCH)) + geom_density() + xlim(0,10000)
p2 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigGCH)) + geom_density() + xlim(0,2000)
p3 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigRCH)) + geom_density() + xlim(0,6000)
p4 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigDRCH)) + geom_density() + xlim(0,2000)

multiplot(p1,p2,p3,p4, cols = 2)

n1 <- nrow(dat)

dat %<>% 
  filter(Intensity_IntegratedIntensity_OrigBCH > 100 & Intensity_IntegratedIntensity_OrigBCH < 7500)
n2 <- nrow(dat)

n1
n2

cells_filtered <- (n1-n2)*100/n1

sprintf("Percentage of cells filtered out: %s", cells_filtered)


p1 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigBCH)) + geom_density() + xlim(0,10000)
p2 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigGCH)) + geom_density() + xlim(0,2000)
p3 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigRCH)) + geom_density() + xlim(0,6000)
p4 <- dat %>% ggplot(aes(Intensity_IntegratedIntensity_OrigDRCH)) + geom_density() + xlim(0,2000)


multiplot(p1,p2,p3,p4, cols = 2)

```


# plot the data - FINAL PLOTS - BCG

```{r, message=FALSE, eval=fit_plots}


ggplot(dat,
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + ylim(0,5000) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles intensity at 02 hpi in BCG",
    y="Whole Cell Int-Intensity of DQ-BSA positive vesicles",
    x="COMPOUND TREATMENT")


ggplot(dat,
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,120) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles count at 02 hpi in BCG",
    y="Count of DQ-BSA positive vesicles",
    x="COMPOUND TREATMENT")


ggplot(dat,
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigDRCH),
           color = Metadata_InfStatus)) + ylim(0,2200) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="Dextran positive vesicles intensity at 02 hpi in BCG",
    y="Whole Cell Int-Intensity of Dextran positive vesicles",
    x="COMPOUND TREATMENT")



ggplot(dat,
         aes(
           x = Metadata_Status,
           y = (Children_DRCH_Count),
           color = Metadata_InfStatus)) + ylim(0,150) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="Dextran positive vesicles count at 02 hpi in BCG",
    y="Count of Dextran positive vesicles",
    x="COMPOUND TREATMENT")


```

# binned intensity plots

```{r, message=FALSE, eval=fit_plots}


dat1 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 0 & Intensity_IntegratedIntensity_OrigRCH < 1000)

dat2 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 1000 & Intensity_IntegratedIntensity_OrigRCH < 2500)

dat3 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 2500 & Intensity_IntegratedIntensity_OrigRCH < 3500)

dat4 <- filter(dat, Intensity_IntegratedIntensity_OrigRCH > 3500 & Intensity_IntegratedIntensity_OrigRCH < 5000)




ggplot(dat1,
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,50) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles count at 02 hpi in BCG",
    y="Count of DQ-BSA positive vesicles in bin 1",
    x="COMPOUND TREATMENT")


ggplot(dat2,
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,120) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles count at 02 hpi in BCG",
    y="Count of DQ-BSA positive vesicles in bin 2",
    x="COMPOUND TREATMENT")


ggplot(dat3,
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,130) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles count at 02 hpi in BCG",
    y="Count of DQ-BSA positive vesicles in bin 3",
    x="COMPOUND TREATMENT")

ggplot(dat4,
         aes(
           x = Metadata_Status,
           y = (Children_RCH_Count),
           color = Metadata_InfStatus)) + ylim(0,130) +
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles count at 02 hpi in BCG",
    y="Count of DQ-BSA positive vesicles in bin 4",
    x="COMPOUND TREATMENT")

#######

ggplot(dat1,
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles intensity at 02 hpi in BCG",
    y="Whole Cell Int-Intensity of DQ-BSA positive vesicles in bin 1",
    x="COMPOUND TREATMENT")


ggplot(dat2,
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles intensity at 02 hpi in BCG",
    y="Whole Cell Int-Intensity of DQ-BSA positive vesicles in bin 2",
    x="COMPOUND TREATMENT")


ggplot(dat3 ,
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) + 
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles intensity at 02 hpi in BCG",
    y="Whole Cell Int-Intensity of DQ-BSA positive vesicles in bin 3",
    x="COMPOUND TREATMENT")


ggplot(dat4,
         aes(
           x = Metadata_Status,
           y = (Intensity_IntegratedIntensity_OrigRCH),
           color = Metadata_InfStatus)) +  
  geom_boxplot(outlier.shape = NA)+
  labs(
    title="DQ-BSA positive vesicles intensity at 02 hpi in BCG",
    y="Whole Cell Int-Intensity of DQ-BSA positive vesicles in bin 4",
    x="COMPOUND TREATMENT")





```
